Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2015-05-24 structured.tex
2015.05.17 (Vassilis) Enabled ancoring for the motivation subsection of the background section. Enabled ancoring for histogram figures (efficiency, overhead, scalability). Elaborated on connection sentences for both (unstructured and structured) discussion sections. Some minor re-wording and image re-scaling for better typesetting.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\emph{3D Overlay (3DO)}~\cite{AOS2014} seeks to address the 
network mismatch problem  for peers operating in mobile networks.
As its name suggests, the network logical space is 
a $3$--$d$ space and the used ``transient'' (continually changing) 
logical \emph{ID}s (\emph{LID}s) consist of $3$ axes, $x$, $y$ and $z$ 
in the form of a tuple;
each such axis value is represented by an $M$-bit identifier.
%%
A newlly-arriving peer broadcasts a join request using
an \emph{TTL}-based expanding ring search helping locate 
peers that are physically adjacent.
Responding peers send in 
their \emph{LID}s along with a list of their neighbors 
and their corresponding distances from those neightbors. 
%%
Once a joining peer receives the above responses,
it stores requisite information in its own routing table 
and so, it generates an undirected connected
graph of itself with both its $1$- and $2$-hop neighbours. 
%%
Starting off this graph and with the help of hop 
distances obtained from the underlying MANET,
the incoming peer builds a minimum spanning tree (MST)
with itself as the root node; 
in this MST, the nodes adjacent to the root become the
direct neighbors of the peer.
%%
Moreover, the entries of the initial routing table 
that do not correspond to above direct neighbors are
eliminated.

@@

Table~\ref{structured:table} offers a comparative view 
on how our surveyed approaches behave.
The topics of topology adaptation, landmarking and caching/replication
are not further elaborated as they have been discussed 
in Section~\ref{section:unstructured}.
In a similar fashion to Table~\ref{unstructured:table}, 
we outline key properties of each surveyed approach 
that helps diffferentiate techniques from competitors.
We also highlight pros and cons for all proposals discussed.

%%AD Connection???  to the groups???
In what follows, we place the surveyed structured \p2p-methods in 
the three categories mentioned above and which are formulated based 
on utilized proximity and geographic aspects.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\emph{3D Overlay (3DO)}~\cite{AOS2014} seeks to address the 
network mismatch problem  for peers operating in mobile networks.
As its name suggests, the network logical space is 
a $3$--$d$ space and the used ``transient'' (continually changing) 
logical \emph{ID}s (\emph{LID}s) consist of $3$ axes, $x$, $y$ and $z$ 
in the form of a tuple;
each such axis value is represented by an $M$-bit identifier.
%%
A newlly-arriving peer broadcasts a join request using
a \emph{TTL}-based expanding ring search helping locate 
peers that are physically adjacent.
Responding peers send in 
their \emph{LID}s along with a list of their neighbors 
and their corresponding distances from those neightbors. 
%%
Once a joining peer receives the above responses,
it stores requisite information in its own routing table 
and so, it generates an undirected connected
graph of itself with both its $1$- and $2$-hop neighbours. 
%%
Starting off this graph and with the help of hop 
distances obtained from the underlying MANET,
the incoming peer builds a minimum spanning tree (MST)
with itself as the root node; 
in this MST, the nodes adjacent to the root become the
direct neighbors of the peer.
%%
Moreover, the entries of the initial routing table 
that do not correspond to above direct neighbors are
eliminated.

@@

%%AD Connection???  to the groups???
%%VM I like it. I put one similar to the unstructured part
In what follows, we place the surveyed structured \p-methods in 
the three categories mentioned above and which are formulated based 
on utilized proximity and geographic aspects.
With Table~\ref{structured:table}, we offer a comparative view
of the algorithms in a similar fashion to Table~\ref{unstructured:table}, 
to outline the key properties of each surveyed approach 
that helps differentiate techniques from
competitors~\footnote{The topics of topology adaptation, landmarking and
caching/replication are not further elaborated as they have been discussed 
in Section~\ref{section:unstructured}.}.
Finally, Figures~\ref{structured:plot:efficiency}, \ref{structured:plot:overhead}
and \ref{structured:plot:scalability} help with the pictorial comparison
of the algorithms' bahavior with respect to the three effectiveness
criteria we defined in Subsection~\ref{background:motivation}.

### 2015-05-24 unstructured.tex
2015.05.17 (Vassilis) Enabled ancoring for the motivation subsection of the background section. Enabled ancoring for histogram figures (efficiency, overhead, scalability). Elaborated on connection sentences for both (unstructured and structured) discussion sections. Some minor re-wording and image re-scaling for better typesetting.

Below, we outline how the proposed protocols use elements of the four
methodologies and we offer a summary qualitative comparison for all surveyed
approaches applicable for \emph{unstructured}~\p~\emph{systems}.
Moreover, Table~\ref{unstructured:table} offers a summary overview for each effort;
in particular, the Table shows which of the aforementioned methodologies 
every effort incorporates, the highlights of the effort as well as 
a rough estimation of the pros and cons of in its implementation.

@@

In landmark-based algorithms, nodes use network delay (e.g., \emph{RTT}) as a
distance measurement method to position themselves with respect to ``a priori''
known servers on the Internet, like \emph{Ono} which uses the \emph{CDN}-infrastructure
for this purpose.
These landmark--servers are used by nodes to estimate 
their positions based on the intuitive assumption that nodes
with similar distances to a set of landmarks, are physically close to each
other, as well, over the network. 
In Figure~\ref{figure:landmarking}, the newly
arriving peer, measures its distance to an array of landmark point denoted as
$L_n$ and and makes a sorted list of the peers, say in increasing order. Then in
order to choose the already participating peers with which to connect to,
the peer compares its list to the list of the potential neighbor. Peers with similar
measured distances to the these landmark points are likely to be close to
each other as well.
%%
\begin{figure}[ht]
\centering
  \includegraphics[scale=0.35]{img/pdf/landmarking.pdf}
\caption{Landmark binning during node bootstrap.}
\label{figure:landmarking}
\end{figure}

>>>>

Below, we outline how the proposed protocols use elements of the above four
methodologies. Then we offer a summary qualitative comparison for all surveyed
approaches applicable for \emph{unstructured}~\p~\emph{systems}.
Specifically, Table~\ref{unstructured:table} summarises, for each
effort, the methodologies it incorporates, its special highlights as well as 
a rough estimation of the pros and cons in its implementation. Last but
not least, with Figures~\ref{unstructured:plot:efficiency}, \ref{unstructured:plot:overhead}
and \ref{unstructured:plot:scalability} we pictorially compare the
algorithms in terms of \emph{efficiency}, \emph{overhead} and \emph{scalability}
respectively; criteria we defined in Subsection~\ref{background:motivation}
and which we used to evaluate the effectiveness of the each surveyed algorithm.

@@

In landmark-based algorithms, nodes use network delay (e.g., \emph{RTT}) as a
distance measurement method to position themselves with respect to ``a priori''
known servers on the Internet, like \emph{Ono} which uses the \emph{CDN}-infrastructure
for this purpose.
For example, in Figure~\ref{figure:landmarking}, the newly
arriving peer, measures its distance to an array of landmark points denoted as
$L_n$. Then it creates an ordered list of the landmarks based on its measured
distances uses that information to select its neighbours. Specifically,
the landmark--servers are used by nodes to estimate 
their positions based on the intuitive assumption that peers
with similar distances to a set of landmarks, are physically close to each
other, as well, over the network.  
%%
\begin{figure}[ht]
\centering
  \includegraphics[scale=0.34]{img/pdf/landmarking.pdf}
\caption{Landmark binning during node bootstrap.}
\label{figure:landmarking}
\end{figure}
